---
title: "Initial HHH4 Models: Meeting Notes"
author: "Bianca Brusco"
date: '2022-05-25'
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(surveillance)
```

Summary and a few plots from the fitted models.

## Model 1: no weights

```{r noweights-fit, eval=FALSE, echo=TRUE}
fit_noweights <-
  surveillance::hhh4(oc_zip_covid)
```

```{r noweights}
fit_noweights <- readRDS("outputs/hhh4_models/noweights.RDS")
summary(fit_noweights)
```

Plots for the model:

```{r noweights-plots, out.width = '70%', fig.show='hold',fig.align='center'}
plot(fit_noweights)
plot(fit_noweights, "map")
```

## Model 2: Sum Weights of Out Visits from Safegraph

```{r sumweights-fit, eval=FALSE, echo=TRUE}
sumweights_nb <- surveillance::hhh4(
  oc_zip_covid,
  control = list(
    ne = list(
      f = ~1,
      weights = neighbourhood(oc_zip_covid),
      family = "NegBin1",
      normalize = TRUE
    )
  )
)
```

```{r sumweights}
sumweights_nb<- readRDS("outputs/hhh4_models/sumweights_nb.RDS")
summary(sumweights_nb)
```

Plots for the model:

```{r sumweights-plots, out.width = '70%',fig.show='hold',fig.align='center'}
plot(sumweights_nb)
plot(sumweights_nb, "map")
```

Can also specify with Poisson link?

```{r sumweights-poi}
sumweights_poi<- readRDS("outputs/hhh4_models/sumweights_poisson.RDS")
summary(sumweights_poi)
```

## Model 3: Binary Neighbours Weights Matrix

From Zip codes adjacency: 0 (not neighbours). 1 (neighbours).

```{r binweights-fit, eval=FALSE, echo=TRUE}
binweights_nb <- surveillance::hhh4(
  oc_zip_covid,
  control = list(
    ne = list(
      f = ~ 1,
      weights = neighbourhood(oc_zip_covid),
      family = "NegBin1",
      normalize = TRUE
    )
  )
)
```

```{r binweights}
binweights_nb<- readRDS("outputs/hhh4_models/binweights_nb.RDS")
summary(binweights_nb)
```

Plots for the model:

```{r binweights-plots, out.width = '70%',fig.show='hold',fig.align='center'}
plot(binweights_nb)
plot(binweights_nb, "map")
```

```{r binweights-poi}
binweights_poi<- readRDS("outputs/hhh4_models/binweights_poisson.RDS")
summary(binweights_poi)
```

**Notes:**

 - Having issues with interpretation of the models.

 - Not all 85 ZIP Codes due to incongruence between the data files. To
be resolved. Currently, these models are based on 74 zip codes.

 - Questions:

 - Visits from outside ZIP code have not been at all considered

 - To do:

 - Time varying weights
